Safe and Robust Formal Synthesis of Digital Controllers for Continuous Plants

### 2018-03-15 automatica/paper.tex
+ preliminaries on CEGIS

\usepackage{graphicx}
\usepackage{color}
\usepackage{amssymb}
\usepackage{amsmath}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{framed}
\usepackage{listings}
\usepackage{algorithm,algpseudocode}
\usepackage{epstopdf}
\usepackage{cite}
\usepackage{pifont}
\usepackage{todonotes}
\usetikzlibrary{positioning, automata, shapes.arrows, calc, shapes, arrows}
\usetikzlibrary{patterns}
\usepackage{url}

@@

@@

%-------------------------------
\section{Counterexample Guided Inductive Synthesis} 
\label{ssec:cegis}
%-------------------------------

%-------------------------------
\subsection{CEGIS of digital controllers} 
\label{sssec:cegisdig}
%-------------------------------

%-------------------------------
\subsubsection{Naive approach} 
\label{sssec:naive}
%-------------------------------

@@

%-------------------------------
\subsubsection{Abstraction-based CEGIS} 
\label{sssec:abstraction}
%-------------------------------

>>>>

\usepackage{graphicx}
\usepackage{color}
\usepackage{amssymb}
\usepackage{amsmath}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{framed}
\usepackage{listings}
\usepackage{algorithm,algpseudocode}
\usepackage{epstopdf}
\usepackage{cite}
\usepackage{pifont}
\usepackage{todonotes}
\usetikzlibrary{positioning, automata, shapes.arrows, calc, shapes, arrows}
\usetikzlibrary{patterns}

\tikzset{
    %Define style for boxes
    box/.style={
           rectangle,
           rounded corners,
           draw=black, very thick,
           fill=yellow!20,
           text width=10em,
           minimum height=2em,
           text centered},
 % 
  futurebox/.style={
           rectangle,
           rounded corners,
           draw=black, very thick,
           fill=blue!10,
           text width=10em,
           minimum height=2em,
           text centered},
 % 
  longfuturebox/.style={
           rectangle,
           rounded corners,
           draw=black, very thick,
           fill=purple!20,
           text width=10em,
           minimum height=2em,
           text centered},
%
    % Define arrow style
    arrow/.style={
           ->,
           thick,
           shorten <=2pt,
           shorten >=2pt,}
}

\usepackage{url}

@@

%-------------------------------
\subsection{State-space representation of physical systems}
\label{sec:model}
%-------------------------------

@@

%-------------------------------
\subsection{Counterexample Guided Inductive Synthesis} 
\label{ssec:cegis}
%-------------------------------

\begin{figure*}
%\hspace{-2cm}
\centering
\resizebox{.57\textwidth}{!}{
 \begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto,
 semithick, initial text=, ampersand replacement=\&,]

  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center
},
          row sep=1cm, column sep=3cm] {
   \node[fill=gray!20] (synth) {{\sc Synthesize}};
   \&
   \node[fill=gray!20] (verif) {{\sc Verify}};
   \&
   \node[ellipse,fill=gray!20] (done) {{\sc Done}}; 
    \\
  };

   \path
   ([yshift=2em]synth.east) edge node[align=center] {Candidate solution} ([yshift=2em]verif.west)
    ([yshift=-2em]verif.west) edge node[align=center] {Counter-example} ([yshift=-2em]synth.east)
    (verif) edge node {} (done);
 \end{tikzpicture}
}
 \caption{The CEGIS framework. \label{fig:CEGIS}}
\end{figure*}

In this section, we give a brief description of the CEGIS framework, as illustrated in Figure~\ref{fig:CEGIS}.

The input specification provided to CEGIS is of the form
$\exists P .\, \forall a.\, \sigma(a, P)$, where $P$ ranges over functions
(where a function is represented by the program computing it),
$a$ ranges over ground terms, and $\sigma$ is a quantifier-free formula. 
We~interpret the ground terms over some finite domain~$\mathcal{D}$.
%

The design of our synthesizer consists of two phases, an inductive
synthesis phase (denoted by {\sc Synthesize} in
Figure~\ref{fig:CEGIS}) and a validation phase (denoted by {\sc
  Verify}), which interact via a finite set of test vectors {\sc
  inputs} that is updated incrementally.  Given the aforementioned
specification $\sigma$, the inductive synthesis procedure tries to
find an existential witness $P$ satisfying the specification
$\sigma(a, P)$ for all $a$ in {\sc inputs} (as opposed to all $a \in
\mathcal{D}$).
%
If the synthesis phase succeeds in finding a witness~$P$, this witness is a
candidate solution to the full synthesis formula.  We pass this candidate
solution to the validation phase, which checks whether it is a full solution
(i.e., $P$ satisfies the specification $\sigma(a, P)$ for all
$a\in\mathcal{D}$).  If this is the case, then the algorithm terminates. 
Otherwise, additional information is provided to the inductive synthesis
phase in the form of a new counterexample that is added to the {\sc inputs}
set and the loop iterates again.  %% More details about the general
%% architecture of the synthesizer can be found
%% in~\cite{DBLP:conf/lpar/DavidKL15}.

%-------------------------------
\section{CEGIS of digital controllers} 
\label{sssec:cegisdig}
%-------------------------------

%-------------------------------
\subsection{Naive approach} 
\label{sssec:naive}
%-------------------------------

@@

%-------------------------------
\subsection{Abstraction-based CEGIS} 
\label{sssec:abstraction}
%-------------------------------
